Weather Data Integration and Assimilation System\\

### 2020-02-15 method/sec_4-db_struct.tex
Grammarly data preprocessing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when new extension creates on \cref{se:data_preprocess}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}

### 2020-02-15 method/sec_5-data_preprocess.tex
Grammarly data preprocessing

The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

The WDIAS provides the support via in build simple generic mathematical function model. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

\subsection{Interpolation}
The Interpolation module generates data at desired locations or at desired points in time by means of either a serial or spatial interpolation technique. It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighbouring locations.

@@

\paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from time series data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

@@

\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Timeseries data validation against set of rules.}}
    \label{fi:validation}
\end{figure}

@@

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's \emph{OnChange} timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

\hl{As an example,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint. First, other than storing extension metadata in MySQL instance of adapter-extension, it also store the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus, the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering need to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in \acrshort{redis} database for fast access and avoid too much queries on \acrshort{mysql} database.

\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at given time which is provided at the creation on extension trigger's with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension expose an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extension which are grouped by cronjob time; within the extension-handler, it schedules programatic cronjobs to trigger at given times. When each cronjob triggers at given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with long period of time in order to avoid heavy overhead.
When a new extension trigger created, those data push into a \acrshort{redis} List. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, in order to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in long period of time and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, in order to avoid triggering same extension twice.

>>>>

The data imported via imported modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
Thus it required to preprocess data before going to use it in such cases. The WDIAS supports these capabilities via Extensions. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

The WDIAS provides the support via a simple generic mathematical function model. Each extension is considering as a mathematical function which can take \texttt{p} number of input timeseries variables and output \texttt{n} number of timeseries variables. Other than that, at the time of processing the system can configure to provide bind constant which can provide while configuring an extension. This means it is possible to change the behavior of an existing function by providing different bind constant at the time of creating new triggers for an extension.

\subsection{Interpolation}
The Interpolation module generates data at desired locations or desired points in time using either a serial or spatial interpolation technique. It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighboring locations.

@@

\paragraph{Spatial Interpolation}-- In spatial interpolation mode, the interpolation can be either applied to fill gaps in time series, or to create a new time series for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar time series from grid time series, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/spatial_interpolation.jpg}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

@@

\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Timeseries data validation against a set of rules.}}
    \label{fi:validation}
\end{figure}

@@

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on the subscribed extension trigger's \emph{OnChange} timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

\hl{As an example,} when new data imported into one of the adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler checks whether there is any extension subscribed for particular timeseries, and triggers it via triggering an event on particular extensions.

To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint. First, other than storing extension metadata in MySQL instance of adapter-extension, it also stores the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus, the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in the \acrshort{redis} database for fast access and avoid too many queries on the \acrshort{mysql} database.

\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension exposes an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extensions which is grouped by cronjob time; within the extension-handler, it schedules programmatic cronjobs to trigger at given times. When each cronjob triggers at the given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
When a new extension trigger created, those data push into a \acrshort{redis} list. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, to avoid triggering the same extension twice.
